Homicide Increases in the COVID-19 Era

### 2025-02-27 Draft1.qmd
completed histogram (plot 1 for draft 2)

crime_la_monthly <- crime_la %>% group_by(Year)
# convert to date
evictions_la$month_year <- format(as.Date(evictions_la$Date.Received, format="%m-%d-%Y"), "%Y-%m")

@@

ggplot(data = evictions_la_indexed, aes(x = index)) + 
  geom_histogram(bins = nrow(unique_months)) +
  scale_x_continuous(breaks=unique_months$index,
        labels=unique_months$month_year) + 
  theme(axis.text.x = element_text(angle = 285, vjust = 0.5, hjust=1),
        axis.title.x = element_text(vjust = -.75),
        plot.title = element_text(size=12)) + 
  labs(x = "Month and Year of Eviction Notice Receipt", y = "Number of Evictions", title = "Monthly Frequency of Evictions in the City of Los Angeles \nFebruary 2023 to February 2025") +

>>>>

# convert to date
evictions_la$month_year <- format(as.Date(evictions_la$Date.Received, format="%m-%d-%Y"), "%Y-%m")

@@

# create color scheme
crime_la$month_year <- format(crime_la$DateParsed, "%Y-%m")
crime_la_monthly <- crime_la %>% 
  group_by(month_year) %>% 
  summarize(num_crimes = n())

avg_crimes <- mean(evictions_la_indexed_crimes$num_crimes)

crime_la_monthly$high_low_crime <- as.factor(ifelse(crime_la_monthly$num_crimes > avg_crimes, "Above Average", "Below Average"))

evictions_la_indexed_crimes <- evictions_la_indexed %>% left_join(crime_la_monthly, by = "month_year")

ggplot(data = evictions_la_indexed_crimes, aes(x = index)) + 
  geom_histogram(aes(fill = high_low_crime), bins = nrow(unique_months)) +
  scale_x_continuous(breaks=unique_months$index,
        labels=unique_months$month_year) + 
  labs(x = "Month and Year of Eviction Notice Receipt", y = "Number of Evictions", title = "Monthly Frequency of Evictions and Crimes in the City of Los Angeles \nFebruary 2023 to February 2025", fill = "Crime Level") +
  ggthemes::scale_fill_fivethirtyeight() + 
  ggthemes::theme_stata(scheme = "s1mono") +
  theme(axis.text.x = element_text(angle = 300, vjust = 0.5, hjust = -.1),
        axis.title.x = element_text(vjust = -.75),
        plot.title = element_text(size=12))
```
### Interpretation
